An Efficient Forecasting Approach\\ to Reduce Boundary Effects in Real-Time Time-Frequency Analysis

### 2021-01-29 Paper/results.tex
minor

{\color{red}
\subsubsection{Two-Component Respiratory Signal}
Then, we consider a second respiratory signal that contains not only the respiratory cycle, but also a cardiac component known as the cardiogenic artifact~\cite{Smith94recognition}. The top of Fig.~\ref{fig:resp.2} shows an excerpt of the measured signal, as well as a 10-second-long {\sf SigExt} extension. Below, the simultaneously recorded ECG signal emphasizes the coincidences between the cardiogenic artifact of the respiratory signal and the ECG.

>>>>

{\color{red}
\subsubsection{Two-Component Respiratory Signal}
Then, we consider a second respiratory signal that contains not only the respiratory cycle, but also a cardiac component known as the cardiogenic artifact~\cite{Smith94recognition}. The top of Fig.~\ref{fig:resp.2} shows an excerpt of the measured signal, along with a 10-second-long {\sf SigExt} extension. Below, the simultaneously recorded ECG signal emphasizes the coincidences between the cardiogenic artifact of the respiratory signal and the QRS complex of the ECG signal.
